\documentclass[]{resume}

\begin{document}
\textrm{\Huge\textcolor{highlight}{\textbf{Saswata Bhunia}}}
\vspace{.4em}

Jalandhar, Punjab | \href{mailto:ow.saswata@gmail.com}{ow.saswata@gmail.com} | 7872055339 | \href{https://www.linkedin.com/in/saswatax}{\faLinkedin \space saswatax} | \href{https://github.com/saswatax}{\faGithub \space saswatax}
\vspace{.4em}

% \section{SUMMARY}
% Full-stack developer with 2 years of hands-on experience in the MERN stack. Proficient in both frontend and backend development, with additional expertise in DevOps and cloud solutions. Enthusiastic about technology and driven to explore new advancements. Seeking opportunities to contribute and grow within a dynamic team.

\section{SKILLS}
\begin{description}
  \item[Frontend:] React, Redux, NextJs, Typescript, Framer Motion, MUI, TailwindCSS, ThreeJs 
  \item[Backend:] NodeJs, Express, MongoDB, Redis, Postgres, SQL, Web Socket, BullMQ, OAuth, JWT, REST API, LangChain, OpenAI, Pinecone, Golang, Go-Chi, gRPC, Python
  \item[DevOps \& Cloud:] Docker, Kubernetes, CI/CD, AWS Lambda, EC2, ECS, S3, SQS, CloudFront
\end{description}

\section{EXPERIENCE}
\elementheader{Software Developer} | \textrm{Outgrow.co}\\
SEP 2022 - Present, Jalandhar, Punjab
\begin{itemize}
  \item Built a live chat interface using OpenAI, tailored with custom knowledge from website scraping data and uploaded documents and made available across various platforms including WhatsApp Business, Facebook Messenger, and web page embedding.
  \item Created a workflow generation tool using OpenAI to automate the creation of marketing workflows, integrating CRM data, LinkedIn, and public domain information to effectively promote products to potential customers.
  \item Implemented Single Sign-On (SSO) authentication using OAuth (PKCE) for Google and Facebook.
  \item Created a node-based drag-and-drop workflow builder with touch support and ARIA compatibility for enhanced accessibility.
  \item Developed a subscription-based payment system utilizing ZOHO Subscription, incorporating features for coupon management and add-ons.
  \item Developed browser extensions compatible with Google Chrome, Firefox, and Safari.
  \item Built multiple AWS Lambda services using AWS CDK to optimize backend load distribution and execute scheduled operations.
  \item Utilized Redis to minimize database queries and implemented features for rate limiting and IP blacklisting.
  \item Managed deployment and maintenance of infrastructure, including writing CI/CD pipelines for continuous development.
  \item Set up development and build tooling to enhance Developer Experience (DX) and reduce build times.
  \item Integrated various third-party tools such as Zapier, Make.com, Twilio, and Gmail to extend functionality and automation capabilities.
\end{itemize}

\section{EDUCATION}
\elementheader{B.Tech in Computer Science} | \textrm{Lovely Professional University}\\
2018 - 2022, Jalandhar, Punjab

\section{PROJECTS}
\elementheader{RSS Aggregator} | \href{https://github.com/saswatax/rss-aggregator}{\faGithub}
\begin{itemize}
  \item An RSS Aggregator that offers user account management, secure API-based authentication, RSS feed creation and subscription, and post aggregation for a seamless and intuitive reading experience.
  \item Tech Stack: Golang, Go-chi, Postgres, REST API
\end{itemize}
\elementheader{Email Client} | \href{https://github.com/saswatax/email-client}{\faGithub}
\begin{itemize}
  \item A unified email client that consolidates multiple accounts (Gmail, Outlook) into one interface, enabling seamless access, management, and sending of emails, with a responsive user interface for optimal display and interaction across devices.
  \item Tech Stack: NextJs, shadcn/ui, Redis
\end{itemize}

\end{document}