\documentclass[]{resume}

\begin{document}
\textrm{\Huge\textcolor{highlight}{\textbf{Saswata Bhunia}}}
\vspace{.4em}

Jalandhar, Punjab | \href{mailto:ow.saswata@gmail.com}{\faEnvelope \space ow.saswata@gmail.com} | \faPhone \space 7872055339 | \href{https://www.linkedin.com/in/saswatax}{\faLinkedin \space saswatax} | \href{https://github.com/saswatax}{\faGithub \space saswatax}
\vspace{.4em}

\section{SUMMARY}
Full-stack developer with 2 years of experience in the MERN stack, building web platforms, APIs, and backend systems. Also experienced in DevOps, handling CI/CD pipelines and cloud deployments.

\section{SKILLS}
\begin{description}
  \item[Frontend:] React, Redux, NextJs, Typescript, Framer Motion, MUI, TailwindCSS, Sass, Webpack, Vite
  \item[Backend:] NodeJs, Express, MongoDB, Redis, PostgreSQL, Web Socket, BullMQ, OAuth, JWT, REST API, Pinecone, Golang, Go-Chi, gRPC
  \item[DevOps \& Cloud:] Docker, Kubernetes, CI/CD, AWS Lambda, EC2, ECS, S3, SQS
\end{description}

\section{EXPERIENCE}
\elementheader{Software Developer} | \textrm{Outgrow.co}\\
SEP 2022 - Present, Jalandhar, Punjab
\begin{itemize}
  \item Led the development of omniengage.co and chatbotbuilder.net, creating both platforms from the ground up, including all backend systems, API structures, and database schemas.
  \item Created a platform for generating RAG-based support bots that utilize custom datasets, such as websites and documents, leveraging OpenAI and Claude models for improved data retrieval and response generation.
  \item Implemented Single Sign-On (SSO) authentication using OAuth (PKCE) for Google and Facebook.
  \item Created a node-based drag-and-drop workflow builder with touch and keyboard control support for enhanced accessibility.
  \item Developed a subscription-based payment system utilizing ZOHO Subscription, incorporating features for coupon management and add-ons.
  \item Built a cross-browser extension to integrate LinkedIn, enabling data extraction and seamless functionality with our platform.
  \item Built multiple AWS Lambda services using AWS CDK to optimize backend load distribution and execute scheduled operations.
  \item Implemented Redis to minimize database queries and added a rate limiting feature.
  \item Managed deployment and maintenance of infrastructure, including writing CI/CD pipelines for continuous development.
  \item Set up development and build tooling to enhance Developer Experience (DX) and reduce build times.
  \item Integrated third-party tools such as Zapier, Make.com, Twilio, Gmail, WhatsApp Business, Intercom, Zendesk and Salesforce to extend functionality and automation capabilities.
\end{itemize}

\section{EDUCATION}
\elementheader{B.Tech in Computer Science} | \textrm{Lovely Professional University}\\
2018 - 2022, Jalandhar, Punjab

\section{PROJECTS}
\elementheader{RSS Aggregator} | \href{https://github.com/saswatax/rss-aggregator}{\faGithub}
\begin{itemize}
  \item An RSS feed aggregator that allows users to create and subscribe to RSS feeds, with account management and secure API-based authentication, providing automatic feed updates.
  \item Tech Stack: Golang, Go-chi, Postgres, REST API
\end{itemize}
\elementheader{Email Client} | \href{https://github.com/saswatax/email-client}{\faGithub}
\begin{itemize}
  \item An email client that integrates multiple email accounts, such as Gmail and Outlook, into a single interface, allowing for effortless email access and management with a responsive user interface.
  \item Tech Stack: NextJs, shadcn/ui, Redis
\end{itemize}

\end{document}